Reading Notes

### 2020-09-09 2pd.tex
contingency

- obj 4 and 5 maybe there aren't descriptors that classify good CT or assemblers? our past work with artificial net has done a better than expected job with p3ht and ct is confidence inspiring but if we dont find the top three-- at least we'll have a dataset that is a stepping stone toward solving but we should be able to generate features of NFAs and polymers
- obj 3 needs models and  access to computational resources. some of the coarse graining and pipelining work might be limited if objective 1 doesn't go to plan but we can still use naiive models like UA bsu, xsede, inl, and local HPC resources inspire confidence that wwe will have adequate resources 
- obj 1 and 2 no specific this stand in the way, stitching together existing software and trying out new approaches. thing that inspires confidence around getting these done is active participation in mosdef, software development enroute to this.

>>>>

No specific obstacles stand in the way of Objectives 1 and 2. 
These objectives involve stitching together existing software and trying out some new approaches.
These objectives will require persistent and efficient code development.
My active participation in MoSDeF and other software development project should inspire confidence that I can complete these objectives.

Objective 3 will require the models from Objective 1 and access to computational resources.
Some of the coarse-graining and pipelining work might be limited if Objective 1 doesn't go to plan, but we can still use naiive models like the united-atom model.
As for computational resources, our lab has access to high-performance computing resources from Boise State University, XSEDE, Idaho National Lab, and our lab's local cluster.
Foregoing any catastrophic hardware failure, we will have adequate resources to complete this objective.

Objectives 4 and 5 rely on the assumption that chemical and morphological features exist to correlate with good charge transfer and robust self assembly.
However, perhaps this assumption is wrong and there simply aren't good descriptors for these outcomes.
Our past work with artificial neural nets has done a better than expected job predicting charge transport in p3ht, which should inspire some confidence.
Even if we dont find the top three features that correlate with charge transport or self assembly, at least we'll have a dataset that is a stepping stone toward answering these questions.
